

\documentclass[11pt, letterpaper, UTF-8]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{verbatim}      
\usepackage{lipsum}           		
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{tabularx}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{indentfirst}

\pagestyle{empty}
\begin{document}

\begin{flushright}
Hudson Duan\\
1728 Parker St.\\
Berkeley, CA 94703\\
+1 (518) 817-2220\\
hudsonduan@gmail.com\\
\end{flushright}
\bigskip
\hspace{4ex}When I was just five years old, my friend who was three years older showed me a game called Warcraft: Orcs and Humans. We would take turns typing in `pot of gold' and sending daemons at the AI's base. As I grew up and looking back now, I can say that Blizzard games were a crucial part of my education. I learned about networking while trying to host games of the original DotA and I have fond memories of listening to Terran Theme 1 part 2 while modding my own custom Starcraft games as a creative outlet outside of school.\\ 

My name is Hudson Duan, 26, and I am applying for a role at Blizzard working in a \textbf{PM capacity}. I have spent the past two years self-employed and working on my own startup business as a mobile/web developer and am looking to transition into a larger company. I have always wondered at what went on at Blizzard and it would be a dream to work there. My skills include a full-stack understanding of software development coupled with a strong independent drive/hustle to get things done; talents acquired through working as a generalist with my co-founder at our two person startup, expanded upon in my resume.\\

Additionally, I have a strong background in eSports and gaming. I attended The International in 2013 and 2014 and play Dota, Starcraft II and Heroes of the Storm regularly. I am familiar with Hearthstone as many of my friends talk about it and I used to play Diablo III and vanilla WoW. In addition to computer games, I play classic N64 games like Zelda and table tops such as Magic the Gathering and Dominion. I watch Twitch regularly and follow the eSports scene in general heavily. Some of my favorite games at the moment to watch are Mario Maker and GTA.\\

I hope this letter gives a glimpse as to what I can bring to Blizzard and shows that I still have much to learn as well. In all my projects so far I strive to bring out the underlying passion and ideals; Blizzard seems like a perfect fit. I can't wait to hear back.\\

\bigskip\bigskip
\noindent With care,\\

\bigskip
\noindent 
\textsc{Hudson}\\

\end{document}  
