

\documentclass[11pt, letterpaper, UTF-8]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{verbatim}      
\usepackage{lipsum}           		
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{tabularx}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{indentfirst}

\pagestyle{empty}
\begin{document}

\begin{flushright}
Hudson Duan\\
1728 Parker St.\\
Berkeley, CA 94703\\
+1 (518) 817-2220\\
hudsonduan@gmail.com\\
\end{flushright}
\bigskip
\hspace{4ex}I grew up in rural upstate NY and my town didn't get our first Whole Foods until just last year. After graduating college and finally on my own, I slowly transitioned into eating seasonally, organic, and local as opposed to the daily meals of fast food, as well as buying high quality products that lasted, as opposed to whatever it was I needed at the time. It's all just a part of growing up.\\ 

My name is Hudson Duan, 25, and I am applying to work for The Honest Company as a \textbf{Project Manager}. I spent the past four years since graduating Duke in 2011 working in various technical capacities at multiple startups, and the last two years building my own (expanded upon in my resume). I have managed and launched numerous products across mobile and web, working up and down the stack. I have consulted for small startups and large corporations, building everything from food service API's to Google Glass apps. \\

I am starting a new adventure in LA and am thrilled at the chance to expand my learning as part of a larger company that still has a startup feel. My role most recently has been that of a product generalist, able to juggle development, design, and management, with the end goal of propelling the company forward towards a clear goal. Some things that may not be present in my resum\'e that I want to highlight:

\bigskip
\begin{tabular}{p{.2in}|p{13cm}}
&\hangindent=2emI skew towards supporting others to success, creating the ideal environments for people to work most efficiently.\\
&\hangindent=2emI am optimistic in input and pessimistic in output, meaning I love entertaining theoretical possibilities but am very strict when it comes to execution.\\
&\hangindent=2emI can step in as a technical band-aid when needed and have a strong mental triaging system for tasks given.\\
\end{tabular}
\bigskip\\
I hope this letter gives a glimpse as to what I can bring to The Honest Company and shows that I still have much to learn as well. In all my projects I strive to bring out the underlying passion and ideals and The Honest Company seems like a perfect fit. I can't wait to hear back.\\
\bigskip\bigskip\\
With care,\\
\\

\bigskip
\noindent 
\textsc{Hudson}\\

\end{document}  
